Ab Initio Effective One-Electron Potentials Revisited: General Theory and Example Applications for Charge-Transfer Energy Calculations

### 2019-05-29 papers/2_oep_technique/paper-r0.tex
Notation of 1-1 ERI unifie
General theory chapter elaborated. Notation revised.

\section{\label{s:2}Effective One-Electron Potentials: General Form}

The one\hyp{}electron potential $v^{\rm eff}({\bf r})$
produced by a certain effective one\hyp{}electron charge density distribution $\rho^{\rm eff}({\bf r})$
is 
%
\begin{equation} \label{e:v-eff}
	v^{\rm eff}({\bf r}) = \int \frac{ \rho^{\rm eff}({\bf r}') }{ \vert {\bf r}' - {\bf r} \vert} d{\bf r}' \;,
\end{equation}
%
where ${\bf r}$ is a spatial coordinate. Formally, the effective density can be expanded in terms of an effective
one\hyp{}particle density matrix represented in a certain basis of orbitals, $\BM{\phi}({\bf r})$,
%
\begin{equation} \label{e:d-spectral}
	\rho^{\rm eff}({\bf r}) = \sum_{\alpha\beta} D_{\alpha\beta}^{\rm eff} 
	\phi_\alpha({\bf r}) \phi_\beta^{*}({\bf r})  \;.
\end{equation}
%
Based on that, the operator form of the effective potential 
can be written as
%
\begin{equation} \label{e:oep-operator}
	\hat{v}^{\rm eff} = \sum_{\alpha\beta} 
	\Ket{\alpha} 
	\left[
	\int
	\hat{J}^{\rm}_{\alpha\beta}({\bf r}) 
	\rho^{\rm eff}({\bf r})
	d{\bf r} 
	\right]
	\Bra{\beta}  
\end{equation}
%
with the Coulomb operator defined by
%
\begin{equation}
	\hat{J}^{\rm}_{\alpha\beta}({\bf r}) f({\bf r}) \equiv
	f({\bf r}) 
	\int
	\frac{ \phi_\alpha^{*}({\bf r}') \phi_\beta({\bf r}') }{ \vert {\bf r}' - {\bf r} \vert} d{\bf r}'
\end{equation}
%
for any one\hyp{}electron function $f({\bf r})$. The matrix element of the effective potential operator
is therefore given by
%
\begin{equation}
	\tBraKet{\alpha}{ \hat{v}^{\rm eff} }{\beta}
	= \sum_{\gamma\delta} \BraKet{\alpha\beta}{\gamma\delta} D^{\rm eff}_{\gamma\delta}  \;.
\end{equation}
%
In the above equation and throughout the work, 
%
\begin{equation}
\tBraKet{\alpha}{\mathcal{O}(1)}{\beta} \equiv \int \phi^*_\alpha({\bf r}) \mathcal{O}(1) \phi_\beta({\bf r}) d{\bf r} 
\end{equation}
%
for any one\hyp{}electron operator $\mathcal{O}(1)$ 
and the electron repulsion integral (ERI)
is defined according to
%
\begin{equation}
	\BraKet{\alpha\beta}{\gamma\delta} \equiv
	\iint 
	\frac{ \phi_\alpha^{*}({\bf r}_1) \phi_\beta({\bf r}_1) 
	       \phi_\gamma^{*}({\bf r}_2) \phi_\delta({\bf r}_2) }{ \vert {\bf r}_1 - {\bf r}_2 \vert}
	d{\bf r}_1 d{\bf r}_2  \;.
\end{equation}
%

@@

An arbitrary one-electron potential of molecule $A$ acting on any state vector 
associated with molecule $A$ can be expanded in an auxiliary space centered 
on $A$ as
%
\begin{equation}
   \hat{v}^{A}\Ket{i} = \sum_{\xi\eta}^{\rm RI} \hat{v}^{A}\Ket{\xi} [{\bf S}^{-1}]_{\xi\eta} \BraKet{\eta}{i}
\end{equation}
%
under the necessary assumption that the auxiliary basis set is nearly complete,
i.e., 
$\sum_{\xi\eta}^{\rm RI} \Ket{\xi}[{\bf S}^{-1}]_{\xi\eta} \Bra{\eta} \cong 1$.
In the equations above, 
the `RI' symbol denotes a certain auxiliary basis set that fulfills the resolution of identity. 
%In a special case when the basis set is orthogonal (e.g., molecular orbitals)
%the above relation simplifies to
%\begin{equation}
%   v\vert i) = \sum_{\xi} v\vert \xi) ( \xi \vert i)
%\end{equation}
Such a general expansion can be obtained by 
utilizing the density fitting
in the nearly\hyp{}complete space,
%
\begin{equation}
 \hat{v}^{A}\Ket{i} = \sum_{\xi}^{\rm RI} V^A_{i\xi} \Ket{\xi} \;.
\end{equation}
%
In the above equation,
the matrix ${\bf V}^A$
is the projection of the state vector $\hat{v}^{A} \Ket{i}$
onto the complete basis $\{ \varphi_\xi \}$.
Let $Z_i[{\bf V}^A]$ be the least\hyp{}squares objective function 
%
\begin{equation} \label{e:z-compl}
 Z_i[{\bf V}^A] = \int \vert \Xi_i({\bf r}) \vert^2 d{\bf r}
\end{equation}
%
with the error density defined by
%
\begin{equation}
 \Xi_i({\bf r}) = v^A({\bf r}) \phi_i({\bf r}) - \sum_\xi^{\rm RI} V^A_{i\xi} \varphi_\xi({\bf r}) \;.
\end{equation}
%
By requiring that
%
\begin{equation} \label{e:z-necessary-requirement}
 \frac{\partial Z_i[{\bf V}^A]}{\partial V^A_{i\mu}} = 0 \text{ for all $\mu$}
\end{equation}
%
one finds the coefficients of the $i$th row of ${\bf V}^A$ to be
%
\begin{equation}
% {\bf v}_i = {\bf a}^{(i)} \cdot {\bf S}^{-1}
  V^A_{i\xi} = \sum_\eta^{\rm RI} [{\bf S}^{-1}]_{\xi\eta} a^{(i)}_\eta \;,
\end{equation}
%
where the auxiliary matrices are given by
%
\begin{subequations}
\begin{align}
 a^{(i)}_\eta &= \int \varphi^*_\eta({\bf r}) \hat{v}^A \phi_i({\bf r}) d{\bf r} \;,\\  
 S_{\eta\xi}  &= \int \varphi^*_\eta({\bf r}) \varphi_\xi({\bf r}) d{\bf r} \;.
\end{align}
\end{subequations}
%
%Since matrix elements of an OEP operator in auxiliary space can be computed 
%in the same way as the matrix elements with any other basis function, 
%one can formally write the following identity
%\begin{equation}
% (X \vert v\vert i) = \sum_{\xi\eta} S_{X \xi} [{\bf S}^{-1}]_{\xi\eta} (\eta\vert v\vert i)
%\end{equation}
%where $ X $ is an arbitrary orbital.
%When the other orbital
%does not belong to molecule $A$ but to the (changing) environment, it is 
%straightforward to compute the resulting matrix element, which is simply given as  
%\begin{equation}
%   (j_{\in B} \vert v^A \vert i_{\in A}) = \sum_\xi {S_{j\xi}} {G_{i\xi}}
%\end{equation}
%where $j$ denotes the other (environmental) basis function.
%
The working formula for $a^{(i)}_\eta$ can be found by applying 
potential form from Eq.~\eqref{e:v-eff}
along with the spectral representation of the effective density from Eq.~\eqref{e:d-spectral} 
which finally gives
%
\begin{equation}
 a^{(i)}_\eta = \sum_{x} W_{\eta i}^{(x)} + 
 \sum_{\alpha\beta} D^A_{\alpha\beta} 
  \BraKet{\alpha\beta}{\eta i} \;.
%  \iint \frac{ \phi_\alpha^*({\bf r}_1)  \phi_\beta({\bf r}_1) \varphi^*_\eta({\bf r}_2) \phi_i({\bf r}_2)}
% {\vert {\bf r}_1 - {\bf r}_2 \vert }
% d{\bf r}_1 d{\bf r}_2
\end{equation}
%

@@

  V^A_{i\xi} = \sum_\eta^{\rm DF} [{\bf A}^{-1}]_{\xi\eta} b^{(i)}_\eta \;,

@@

 A_{\eta\xi}  &= \iint 

@@

Note that, while $A_{\eta\xi}$ is a typical 2\hyp{}center ERI 

@@

 b^{(i)}_\eta = \sum_\varepsilon^{\rm Int} H_{i\varepsilon} R_{\varepsilon\eta} 

@@

with
 R_{\varepsilon\eta} \equiv \iint 
                       \frac{ \varphi^*_\varepsilon({\bf r}_1) \varphi_\eta({\bf r}_2) } 
                 d{\bf r}_1 d{\bf r}_2 \;,
which can be easily evaluated and the matrix elements of the OEP operator found
from Eq.~\eqref{e:v-noncompl}.

@@

As an illustration of application of the OEP technique for efficient calculation 
of CT energy we consider the second\hyp{}order perturbation theory of Murrell et al.,
in which the energy associated with the charge transfer from molecule $A$ to $B$ is given by
%
\begin{equation} \label{e:ct-murell-etal.e}
 E^{A\rightarrow B} = 2 \sum_{i\in A}^{\rm Occ} \sum_{n\in B}^{\rm Vir} 
  \frac{\vert V^{A\rightarrow B}_{in} \vert^2 }{\varepsilon_i - \varepsilon_n}
\end{equation}
%
%coupling constants between occupied and virtual molecular orbitals 
%are re-expressed by the effective one-electron potentials. The resulting formula provides new possibilities 
%of optimization and applications in condensed phase simulations. [3]
%
where $\varepsilon_i$ and $\varepsilon_n$ are the canonical energies
of the occupied (denoted by `Occ') and virtual (denoted by `Vir') 
HF molecular orbitals, respectively,
whereas the coupling constant is given by
%
\begin{multline} \label{e:ct-murell-etal.vin}
 V^{A\rightarrow B}_{in} = 
        \tBraKet{i}{\hat{v}^B_{\rm tot} }{n} 
      - \sum_{j\in B}^{\rm Occ} \BraKet{nj}{ij} 
      - \sum_{k\in A}^{\rm Occ} S_{nk} \tBraKet{k}{\hat{v}^B_{\rm tot} }{i} \\
      - \sum_{j\in B}^{\rm Occ} S_{ij} \tBraKet{j}{\hat{v}^A_{i} }{n}  
     + \sum_{k\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}  
        S_{kj} \left( 1 - \delta_{ik} \right) 
        \BraKet{nj}{ik} \;.
\end{multline}
%
In the above expression, the following effective potentials,
%
\begin{subequations} 
\begin{align} \label{e:ct-murell-etal.vtot-vi}
 \hat{v}^B_{\rm tot} &= \hat{v}^B_{\rm nuc} + 2\sum_{j\in B}^{\rm Occ} \hat{v}^B_{jj} \quad\text{ and }\\ 
 \hat{v}^A_{i      } &= \hat{v}^A_{\rm tot} - 2\hat{v}^A_{ii} \;,
\end{align}
\end{subequations}
%
were introduced without making any approximation to the original equation
from Ref. One can immediately notice that the five summation terms
from Eq.~\eqref{e:ct-murell-etal.vin} can be classified into three groups
regarding the type of ERI's that are required:
(i) $\BraKet{AB}{BB}$ -- the first two terms;
(ii) $\BraKet{AA}{BB}$ -- the third term and
(iii) $\BraKet{BB}{AA}$ -- the two last terms. 
%Note that groups (ii) and (iii) correspond to the Coulomb interactions between
%The group (i) corresponds to the overlap\hyp{}like integrals, whereas the groups (ii) and (iii)
%correspond to the Coulomb\hyp{}like integrals

\paragraph{Group (i).}
Group (i) can be rewritten by noticing that
%
\begin{equation} \label{e:ct-murell-etal.group-i.notice}
 \sum_{j\in B}^{\rm Occ} 
 \BraKet{nj}{ij} =
 \Bra{i} \left[ \hat{v}^B_{nj} \Ket{j} \right]  \;,
\end{equation}
%
which, by combining with the first term from Eq.~\eqref{e:ct-murell-etal.vin}, 
allows to apply the density fitting in an
incomplete basis set as follows
%
\begin{equation}
\Bra{i} \left[ \hat{v}^B_{\rm tot} \Ket{n} - \sum_{j\in B}^{\rm Occ} \hat{v}^B_{nj} \Ket{j} \right]
\cong \Bra{i} \sum_{\eta\in B}^{\rm DF} V^B_{n\eta} \Ket{\eta}
\end{equation}
%
with the error density defined by
%
\begin{multline}
 \Xi_n({\bf r}) = 
  \left\{
      v_{nuc}^B({\bf r}) + 2 \sum_{j\in B}^{\rm Occ}
   \int \frac{ \vert \phi_j({\bf r}') \vert^2 }{\vert {\bf r}' - {\bf r} \vert} d{\bf r}'
  \right\}
  \phi_n({{\bf r}})  \\
 - \sum_{j\in B}^{\rm Occ} \phi_j({{\bf r}})
   \int \frac{ \phi^*_n({\bf r}') \phi_j({{\bf r}'}) }{\vert {\bf r}' - {\bf r} \vert} d{\bf r}'
 - \sum_{\eta\in B}^{\rm DF} V^B_{n\eta} \varphi_\eta({\bf r}) \;.
\end{multline}
%
Substituting the above equation into Eq.~\eqref{e:z-incompl}
%and then
%using resolution of identity to simplify the 
leads to
%
\begin{equation}
 V^B_{n\xi} = \sum_{\eta\in B}^{\rm DF} \left[ {\bf A}^{-1} \right]_{\xi\eta} b_\eta^{(n)} \;,
\end{equation}
%
where
%
\begin{multline}
 b^{(n)}_\eta = \iint 
           d{\bf r}_1 d{\bf r}_2  
           \frac{ \varphi^*_\eta({\bf r}_1) }
            {\vert {\bf r}_1 - {\bf r}_2 \vert } \\ \times
          \left[ 
           \hat{v}^B_{\rm tot}  \phi_n({\bf r}_2) 
         - \sum_{j\in B}^{\rm Occ} \hat{v}^B_{nj} \phi_j({{\bf r}_2})
           \right]  \;.
\end{multline}
%
The above result is given by a sum of triple integrals from Eq.~\eqref{e:triple-integral}.
However, the following application of the resolution of identity,
%
\begin{equation}
 \hat{v}^B_{\rm tot} \Ket{n} - \sum_{j\in B}^{\rm Occ} \hat{v}^B_{nj} \Ket{j}
 \cong \sum_{\varepsilon\in B}^{\rm RI} H_{n\varepsilon}^B \Ket{\varepsilon} \;,
\end{equation}
%
leads to a much simpler formula
that requires only the one- and two\hyp{}electron integrals. 
Therefore, by combining
equations %which equations?
one arrives to
%
\begin{equation}
 V^B_{n\xi} = \sum_{\eta\in B}^{\rm DF} 
          \sum_{\varepsilon\in B}^{\rm RI}
         \left[ {\bf A}^{-1} \right]_{\xi\eta}
         H_{n\varepsilon}^B R_{\varepsilon \eta} \;,
\end{equation}
%
where
%
\begin{equation}
 H_{n\varepsilon}^B = \sum_{\eta\in B}^{\rm RI} \left[ {\bf S}^{-1} \right]_{\varepsilon\eta}
   a_\eta^{(n)}
\end{equation}
%
and
%%
\begin{align}
 a^{(n)}_\eta &= \tBraKet{\eta}{\hat{v}^B_{\rm tot}}{n}
      - \sum_{j\in B}^{\rm Occ} \tBraKet{\eta}{\hat{v}^B_{nj}}{j} \nonumber \\
 &= \sum_{y\in B} W^{(y)}_{\eta n} 
  + \sum_{j\in B}^{\rm Occ} 
  \left\{
   2\BraKet{\eta n}{jj} - \BraKet{\eta j}{nj} 
  \right\} \;.
\end{align}
%
Note that all the calculations that are required to obtain $V^B_{n\xi}$ are performed
solely on the densities and basis sets associated with the unperturbed molecule $B$.
Therefore, $V^B_{n\xi}$ can be considered as effective fragment parameters
used to compute the first two terms of Eq.~\eqref{e:ct-murell-etal.vin} by
%
\begin{equation}
        \tBraKet{i}{\hat{v}^B_{\rm tot} }{n} 
      - \sum_{j\in B}^{\rm Occ} \BraKet{nj}{ij} 
       = \sum_{\eta\in B}^{\rm RI} V^B_{n\eta} S_{\eta i} \;,
\end{equation}
%
which is a great simplification over the original form of group (i)
because only the overlap integrals between the $i$th MO on molecule $A$
and $\eta$th auxiliary orbital on molecule $B$ need to be evaluated on the fly.
Note that the only approximation made so far was the application of density fitting
and resolution of identity. If the auxiliary and intermediate
basis sets are sufficiently large, the errors
due to this approximation can be minimal and negligible.

>>>>

\section{\label{s:2}Effective One-Electron Potentials: General Theory}

The one\hyp{}electron potential $v^{\rm eff}({\bf r})$
produced by a certain effective one\hyp{}electron charge density distribution $\rho^{\rm eff}({\bf r})$
is 
%
\begin{equation} \label{e:v-eff}
	v^{\rm eff}({\bf r}) = \int \frac{ \rho^{\rm eff}({\bf r}') }{ \vert {\bf r}' - {\bf r} \vert} d{\bf r}' \;,
\end{equation}
%
where ${\bf r}$ is a spatial coordinate. 
For convenience, the total effective density can be split into nuclear and electronic contributions,
%
\begin{equation} \label{e:rho-eff}
 \rho^{\rm eff}({\bf r}) = \lambda \rho^{\rm eff}_{\rm nuc}({\bf r}) + \rho^{\rm eff}_{\rm el}({\bf r}) \;,
\end{equation}
%
where $\lambda$ is a certain parameter and is assumed either 1 or 0 in this work.
Formally, the electronic part can be expanded in terms of an effective
one\hyp{}particle density matrix represented in a certain basis of orbitals, $\BM{\phi}({\bf r})$,
%
\begin{equation} \label{e:d-spectral}
	\rho^{\rm eff}_{\rm el}({\bf r}) = \sum_{\alpha\beta} D_{\alpha\beta}^{\rm eff} 
	\phi_\alpha({\bf r}) \phi_\beta^{*}({\bf r})  \;.
\end{equation}
%
Based on that, the operator form of the effective potential 
can be written as
%
\begin{equation} \label{e:oep-operator}
	\hat{v}^{\rm eff} = 
        \lambda \hat{v}_{\rm nuc} +
        \sum_{\alpha\beta} 
	\Ket{\alpha} 
	\left[
	\int
	\hat{J}^{\rm}_{\alpha\beta}({\bf r}) 
	\rho^{\rm eff}({\bf r})
	d{\bf r} 
	\right]
	\Bra{\beta}  
\end{equation}
%
with the nuclear
and Coulomb operators defined by
%
\begin{subequations}
\begin{align}
        \hat{v}_{\rm nuc} &\equiv \\
	\hat{J}^{\rm}_{\alpha\beta}({\bf r}) f({\bf r}) &\equiv
	f({\bf r}) 
	\int
	\frac{ \phi_\alpha^{*}({\bf r}') \phi_\beta({\bf r}') }{ \vert {\bf r}' - {\bf r} \vert} d{\bf r}'
\end{align}
\end{subequations}
%
for any one\hyp{}electron function $f({\bf r})$. The matrix element of the effective potential operator
is therefore given by
%
\begin{equation}
	\tBraKet{\alpha}{ \hat{v}^{\rm eff} }{\beta}
	= \lambda \sum_x^{\rm At} W_{\alpha\beta}^{(x)} +
        \sum_{\gamma\delta} \BraKet{\alpha\beta}{\gamma\delta} D^{\rm eff}_{\gamma\delta}  \;,
\end{equation}
%
where 
%
\begin{equation}
 W_{\alpha\beta}^{(x)} = 
 Z_x \int \frac{\phi^*_\alpha({\bf r}) \phi_\beta({\bf r})}{\vert {\bf r} - {\bf r}_x \vert} d{\bf r} \;,
\end{equation}
%
$Z_x$ is the atomic number of the $x$th atom,
and the symbol `At' denotes all atoms that contribute to the effective potential.
In the above equation and throughout the work, 
%
\begin{equation}
\tBraKet{\alpha}{\mathcal{O}(1)}{\beta} \equiv \int \phi^*_\alpha({\bf r}) \mathcal{O}(1) \phi_\beta({\bf r}) d{\bf r} 
\end{equation}
%
for any one\hyp{}electron operator $\mathcal{O}(1)$ 
and the electron repulsion integral (ERI)
is defined according to
%
\begin{equation}
	\BraKet{\alpha\beta}{\gamma\delta} \equiv
	\iint 
	\frac{ \phi_\alpha^{*}({\bf r}_1) \phi_\beta({\bf r}_1) 
	       \phi_\gamma^{*}({\bf r}_2) \phi_\delta({\bf r}_2) }{ \vert {\bf r}_1 - {\bf r}_2 \vert}
	d{\bf r}_1 d{\bf r}_2  \;.
\end{equation}
%

@@

An arbitrary one-electron potential of molecule $A$ acting on any state vector 
associated with molecule $A$ can be expanded in an auxiliary space centered 
on $A$ as
%
\begin{equation}
   \hat{v}^{A}\Ket{i} = \sum_{\xi\eta}^{\rm RI} \hat{v}^{A}\Ket{\xi} [{\bf S}^{-1}]_{\xi\eta} \BraKet{\eta}{i}
\end{equation}
%
under the necessary assumption that the auxiliary basis set is nearly complete,
i.e., 
$\sum_{\xi\eta}^{\rm RI} \Ket{\xi}[{\bf S}^{-1}]_{\xi\eta} \Bra{\eta} \cong 1$.
In the equations above, 
the `RI' symbol denotes a certain auxiliary basis set that fulfills the resolution of identity. 
%In a special case when the basis set is orthogonal (e.g., molecular orbitals)
%the above relation simplifies to
%\begin{equation}
%   v\vert i) = \sum_{\xi} v\vert \xi) ( \xi \vert i)
%\end{equation}
Such a general expansion can be obtained by 
utilizing the density fitting
in the nearly\hyp{}complete space,
%
\begin{equation}
 \hat{v}^{A}\Ket{i} = \sum_{\xi}^{\rm RI} V^A_{i\xi} \Ket{\xi} \;.
\end{equation}
%
In the above equation,
the matrix ${\bf V}^A$
is the projection of the state vector $\hat{v}^{A} \Ket{i}$
onto the complete basis $\{ \varphi_\xi \}$.
Let $Z_i[{\bf V}^A]$ be the least\hyp{}squares objective function 
%
\begin{equation} \label{e:z-compl}
 Z_i[{\bf V}^A] = \int \vert \Xi_i({\bf r}) \vert^2 d{\bf r}
\end{equation}
%
with the error density defined by
%
\begin{equation}
 \Xi_i({\bf r}) = v^A({\bf r}) \phi_i({\bf r}) - \sum_\xi^{\rm RI} V^A_{i\xi} \varphi_\xi({\bf r}) \;.
\end{equation}
%
By requiring that
%
\begin{equation} \label{e:z-necessary-requirement}
 \frac{\partial Z_i[{\bf V}^A]}{\partial V^A_{i\mu}} = 0 \text{ for all $\mu$}
\end{equation}
%
one finds the coefficients of the $i$th row of ${\bf V}^A$ to be
%
\begin{equation} \label{e:gdf-coml.v}
% {\bf v}_i = {\bf a}^{(i)} \cdot {\bf S}^{-1}
  V^A_{i\xi} = \sum_\eta^{\rm RI} [{\bf S}^{-1}]_{\xi\eta} a^{(i)}_\eta \;,
\end{equation}
%
where the auxiliary matrices are given by
%
\begin{subequations}
\begin{align}
 a^{(i)}_\eta &= \int \varphi^*_\eta({\bf r}) \hat{v}^A \phi_i({\bf r}) d{\bf r} \;,\\  
 S_{\eta\xi}  &= \int \varphi^*_\eta({\bf r}) \varphi_\xi({\bf r}) d{\bf r} \;.
\end{align}
\end{subequations}
%
%Since matrix elements of an OEP operator in auxiliary space can be computed 
%in the same way as the matrix elements with any other basis function, 
%one can formally write the following identity
%\begin{equation}
% (X \vert v\vert i) = \sum_{\xi\eta} S_{X \xi} [{\bf S}^{-1}]_{\xi\eta} (\eta\vert v\vert i)
%\end{equation}
%where $ X $ is an arbitrary orbital.
%When the other orbital
%does not belong to molecule $A$ but to the (changing) environment, it is 
%straightforward to compute the resulting matrix element, which is simply given as  
%\begin{equation}
%   (j_{\in B} \vert v^A \vert i_{\in A}) = \sum_\xi {S_{j\xi}} {G_{i\xi}}
%\end{equation}
%where $j$ denotes the other (environmental) basis function.
%
The working formula for $a^{(i)}_\eta$ can be found by applying 
potential form from Eq.~\eqref{e:v-eff}
along with the spectral representation of the effective density from Eq.~\eqref{e:d-spectral} 
which finally gives
%
\begin{equation}
 a^{(i)}_\eta = \lambda \sum_{x} W_{\eta i}^{(x)} + 
 \sum_{\alpha\beta} D^A_{\alpha\beta} 
  \BraKet{\alpha\beta}{\eta i} \;.
%  \iint \frac{ \phi_\alpha^*({\bf r}_1)  \phi_\beta({\bf r}_1) \varphi^*_\eta({\bf r}_2) \phi_i({\bf r}_2)}
% {\vert {\bf r}_1 - {\bf r}_2 \vert }
% d{\bf r}_1 d{\bf r}_2
\end{equation}
%

@@

  V^A_{i\xi} = \sum_\eta^{\rm DF} [{\bf R}^{-1}]_{\xi\eta} b^{(i)}_\eta \;,

@@

 R_{\eta\xi}  &= \iint 

@@

Note that, while $R_{\eta\xi}$ is a typical 2\hyp{}center ERI 

@@

 b^{(i)}_\eta = \sum_\varepsilon^{\rm RI} H_{i\varepsilon} R_{\varepsilon\eta} \;,

@@

%with
%%
%\begin{equation}
% R_{\varepsilon\eta} \equiv \iint 
%                       \frac{ \varphi^*_\varepsilon({\bf r}_1) \varphi_\eta({\bf r}_2) } 
%                            {\vert {\bf r}_1 - {\bf r}_2\vert}  
%                 d{\bf r}_1 d{\bf r}_2 \;,
%\end{equation}
%%
which can be easily evaluated by noting that
$H_{i\varepsilon}$ are given by Eq.~\eqref{e:gdf-coml.v}.
Thus, the matrix elements of the OEP operator can be found
by using Eq.~\eqref{e:v-noncompl}.

@@

As an illustration of application of the OEP technique for efficient calculation 
of CT energy we consider the second\hyp{}order perturbation theory of Murrell et al.,
in which the energy associated with the charge transfer from molecule $A$ to $B$ is given by
%
\begin{equation} \label{e:ct-murell-etal.e}
 E^{A\rightarrow B} = 2 \sum_{i\in A}^{\rm Occ} \sum_{n\in B}^{\rm Vir} 
  \frac{\vert V^{A\rightarrow B}_{in} \vert^2 }{\varepsilon_i - \varepsilon_n}
\end{equation}
%
%coupling constants between occupied and virtual molecular orbitals 
%are re-expressed by the effective one-electron potentials. The resulting formula provides new possibilities 
%of optimization and applications in condensed phase simulations. [3]
%
where $\varepsilon_i$ and $\varepsilon_n$ are the canonical energies
of the occupied (denoted by `Occ') and virtual (denoted by `Vir') 
HF molecular orbitals, respectively,
whereas the coupling constant is given by
%
\begin{multline} \label{e:ct-murell-etal.vin}
 V^{A\rightarrow B}_{in} = 
        \tBraKet{i}{\hat{v}^B_{\rm tot} }{n} 
      - \sum_{j\in B}^{\rm Occ} \BraKet{nj}{ij} 
      - \sum_{k\in A}^{\rm Occ} S_{nk} \tBraKet{k}{\hat{v}^B_{\rm tot} }{i} \\
      - \sum_{j\in B}^{\rm Occ} S_{ij} \tBraKet{j}{\hat{v}^A_{i} }{n}  
     + \sum_{k\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}  
        S_{kj} \left( 1 - \delta_{ik} \right) 
        \BraKet{nj}{ik} \;.
\end{multline}
%
In the above expression, the following effective potentials,
%
\begin{subequations} 
\begin{align} \label{e:ct-murell-etal.vtot-vi}
 \hat{v}^B_{\rm tot} &= \hat{v}^B_{\rm nuc} + 2\sum_{j\in B}^{\rm Occ} \hat{v}^B_{jj} \quad\text{ and }\\ 
 \hat{v}^A_{i      } &= \hat{v}^A_{\rm tot} - 2\hat{v}^A_{ii} \;,
\end{align}
\end{subequations}
%
were introduced without making any approximation to the original equation
from Ref. One can immediately notice that the five summation terms
from Eq.~\eqref{e:ct-murell-etal.vin} can be classified into three groups
regarding the type of ERI's that are required:
(i) $\BraKet{AB}{BB}$ -- the first two terms;
(ii) $\BraKet{AA}{BB}$ -- the third term and
(iii) $\BraKet{BB}{AA}$ -- the two last terms. 
Note also that there are no exchange\hyp{}like terms needed in this case.
Therefore, all the contributions can be re\hyp{}cast in terms of the OEP's.
%Note that groups (ii) and (iii) correspond to the Coulomb interactions between
%The group (i) corresponds to the overlap\hyp{}like integrals, whereas the groups (ii) and (iii)
%correspond to the Coulomb\hyp{}like integrals

\paragraph{Group (i).}
Group (i) can be rewritten by noticing that
%
\begin{equation} \label{e:ct-murell-etal.group-i.notice}
 \sum_{j\in B}^{\rm Occ} 
 \BraKet{nj}{ij} =
 \Bra{i} \left[ \hat{v}^B_{nj} \Ket{j} \right]  \;,
\end{equation}
%
which, by combining with the first term from Eq.~\eqref{e:ct-murell-etal.vin}, 
allows to apply the density fitting in an
incomplete basis set as follows
%
\begin{equation}
\Bra{i} \left[ \hat{v}^B_{\rm tot} \Ket{n} - \sum_{j\in B}^{\rm Occ} \hat{v}^B_{nj} \Ket{j} \right]
\cong \Bra{i} \sum_{\eta\in B}^{\rm DF} V^B_{n\eta} \Ket{\eta}
\end{equation}
%
with the error density defined by
%
\begin{multline}
 \Xi_n({\bf r}) = 
  \left\{
      v_{nuc}^B({\bf r}) + 2 \sum_{j\in B}^{\rm Occ}
   \int \frac{ \vert \phi_j({\bf r}') \vert^2 }{\vert {\bf r}' - {\bf r} \vert} d{\bf r}'
  \right\}
  \phi_n({{\bf r}})  \\
 - \sum_{j\in B}^{\rm Occ} \phi_j({{\bf r}})
   \int \frac{ \phi^*_n({\bf r}') \phi_j({{\bf r}'}) }{\vert {\bf r}' - {\bf r} \vert} d{\bf r}'
 - \sum_{\eta\in B}^{\rm DF} V^B_{n\eta} \varphi_\eta({\bf r}) \;.
\end{multline}
%
Substituting the above equation into Eq.~\eqref{e:z-incompl}
%and then
%using resolution of identity to simplify the 
leads to
%
\begin{equation}
 V^B_{n\xi} = \sum_{\eta\in B}^{\rm DF} \left[ {\bf R}^{-1} \right]_{\xi\eta} b_\eta^{(n)} \;,
\end{equation}
%
where
%
\begin{multline}
 b^{(n)}_\eta = \iint 
           d{\bf r}_1 d{\bf r}_2  
           \frac{ \varphi^*_\eta({\bf r}_1) }
            {\vert {\bf r}_1 - {\bf r}_2 \vert } \\ \times
          \left[ 
           \hat{v}^B_{\rm tot}  \phi_n({\bf r}_2) 
         - \sum_{j\in B}^{\rm Occ} \hat{v}^B_{nj} \phi_j({{\bf r}_2})
           \right]  \;.
\end{multline}
%
The above result is given by a sum of triple integrals from Eq.~\eqref{e:triple-integral}.
However, the following application of the resolution of identity,
%
\begin{equation}
 \hat{v}^B_{\rm tot} \Ket{n} - \sum_{j\in B}^{\rm Occ} \hat{v}^B_{nj} \Ket{j}
 \cong \sum_{\varepsilon\in B}^{\rm RI} H_{n\varepsilon}^B \Ket{\varepsilon} \;,
\end{equation}
%
leads to a much simpler formula
that requires only the one- and two\hyp{}electron integrals. 
Therefore, by combining
equations %which equations?
one arrives to
%
\begin{equation}
 V^B_{n\xi} = \sum_{\eta\in B}^{\rm DF} 
          \sum_{\varepsilon\in B}^{\rm RI}
         \left[ {\bf R}^{-1} \right]_{\xi\eta}
         R_{\eta \varepsilon} 
         H_{n\varepsilon}^B \;,
\end{equation}
%
where
%
\begin{equation}
 H_{n\varepsilon}^B = \sum_{\zeta\in B}^{\rm RI} \left[ {\bf S}^{-1} \right]_{\varepsilon\zeta}
   a_\zeta^{(n)}
\end{equation}
%
and
%%
\begin{align}
 a^{(n)}_\zeta &= \tBraKet{\zeta}{\hat{v}^B_{\rm tot}}{n}
      - \sum_{j\in B}^{\rm Occ} \tBraKet{\zeta}{\hat{v}^B_{nj}}{j} \nonumber \\
 &= \sum_{y\in B} W^{(y)}_{\zeta n} 
  + \sum_{j\in B}^{\rm Occ} 
  \left\{
   2\BraKet{\zeta n}{jj} - \BraKet{\zeta j}{nj} 
  \right\} \;.
\end{align}
%
Note that all the calculations that are required to obtain $V^B_{n\xi}$ are performed
solely on the densities and basis sets associated with the unperturbed molecule $B$.
Therefore, $V^B_{n\xi}$ can be considered as effective fragment parameters
used to compute the first two terms of Eq.~\eqref{e:ct-murell-etal.vin} by
%
\begin{equation} \label{e:ct.group-i.final}
        \tBraKet{i}{\hat{v}^B_{\rm tot} }{n} 
      - \sum_{j\in B}^{\rm Occ} \BraKet{nj}{ij} 
       = \sum_{\eta\in B}^{\rm RI} V^B_{n\eta} S_{\eta i} \;,
\end{equation}
%
which is a great simplification over the original form of group (i)
because only the overlap integrals between the $i$th MO on molecule $A$
and $\eta$th auxiliary orbital on molecule $B$ need to be evaluated on the fly.
Note that the only approximation made so far was the application of density fitting
and resolution of identity. If the auxiliary and intermediate
basis sets are sufficiently large, the errors
due to this approximation can be minimal and negligible.
